Pillar 1 - Sequential Pattern Mining

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
minor change

  ungroup()
```
####Save d_transactions
```{r save d_transaction}
save(
  d_transactions,
  file = "Output/transaction_df.RDATA"
  )
```
### Transcript with preceding courses (for SR by hand)
```{r d_transcript_cum, cache = TRUE, warning = FALSE}
d_transcript_cum <- d_transactions$taken_PF_HL %>%

>>>>

  ungroup()
```

#### Save d_transactions
```{r save d_transaction}
save(d_transactions, file = "Output/transaction_df.RDATA")
```

### Transcript with preceding courses (for SR by hand)
```{r d_transcript_cum, cache = TRUE}
d_transcript_cum <- d_transactions$taken_PF_HL %>%
